ArborVote -- Deliberative Decision-Making using Argument Trees \deleted[comment={Discuss multiple ways of determining the impact}]{and Rating Markets}

### 2021-08-20 Paper.tex
Applied minor corrections.

\newcommand{\T}{\text{T}}\newcommand{\debateTokens}{debate tokens}
\newcommand{\Y}{\text{Y}}
\newcommand{\N}{\text{N}}

@@

\begin{acronym}
	\acro{AMM}{automated marker maker}
	\acro{PM}{prediction market}
	\acro{RM}{rating market}
	\acro{DAPP}{decentralized application}
	\acro{DAO}{decentralized autonomous organization}
	\acro{DLT}{distributed ledger technology}
	\acroplural{DLT}[DLTs]{distributed ledger technologies}
	\acro{DAG}{directed acyclic graph}
	\acro{MACI}{minimal anti-collusion infrastructure}
	\acro{L2}{layer 2}
\end{acronym}

@@

% Why Blockchain
Since digital debating platforms (such as \href{https://www.kialo.com/}{kialo} do exist online,
the question might arise why \acp{DLT} are needed to construct and execute a decision from a debate.
%
Three requirements favor the usage of \acp{DLT}.
% Tamper-Proof Infrastructure
First and foremost, voting processes require a tamper-proof and permissionless infrastructure that cannot be guaranteed with centralized technologies.
% Sybil protection
A second requirement is Sybil protection. 
Curated registries of unique digital identities are already available on several blockchains. 
% Incentivization
A last and optional requirement is the ability to incentivize participation.
Because the time and collective attention of the people is scarce resources,
the ability to allocate reputational or monetary rewards is useful
and especially easy to realize in the form of blockchain tokens.
To put this economic view in perspective:
One might see this deliberative decision-making as the decentralization of the job of politicians and consultants that are also getting paid.

@@

\section{Structuring Debates in Argument Graphs}\label{sec:Structure}
The reasoning behind making a decision is rarely linear. 
Most of the time, debates consist of multiple, nested arguments
forming threads forking off multiple times being directed towards the root node. 
%
This results in a tree structure as depicted in \cref{fig:Tree},
where arguments constitute the nodes of the tree.
%
Three node types exist in the debate graph: 
root, argument, and fact nodes. 
Nodes without child-nodes below them are called leaves.

\begin{figure}
	\resizebox{0.95\linewidth}{!}{
		\includegraphics{Graphics/Tree.tikz}
	}
	\caption{
		Visualization of a debate as an argument tree with 
		the root node (dotted) $\Root$, 
		argument nodes (solid) $\Arg$, and 
		fact nodes (dashed) $\Fact$
		numbered by their order of creation.
		Nodes have an impact $\imp$ and a weight $\wgt$ relative to their siblings 
		and can support or oppose their associated parent as indicated by green and red links, respectively.
	}
	\label{fig:Tree}
\end{figure}

\subsection{Root Nodes}
The decision option forms the root $\Root$ of the tree and is expressed as a statement that will ultimately be
%supported 
approved 
or 
%opposed %
disapproved 
by the participants of the debate, e.g., 'We should execute process A.'. 
%
To facilitate multiple decision options, multiple trees can be constructed%
---all of them having their own root statement, e.g., 'We should execute process B.', etc.).

\subsection{Argument Nodes}
%\todo{
%	People can create arguments $\Arg[i][k]$, $k>0$.
%	An argument $\Arg[i][k]$ can have multiple child arguments
%	whose indices we collect in the set $\Children[i][k]=\{c_1, c_2, \dots\}$.
%	Likewise, we collect the indices of its direct siblings in the set $\Siblings[i][k]=\{s_1, s_2, \dots\}$.
%}
%\todo{Clarify}
Participants of the debate can create arguments $\Arg$ below the root
or other arguments. 
%
Within a debate, each argument points to one parent node (either the root or another argument) it is referring to.

To identify each node $\Node$ in the tree, we introduce the notation $\Node[i][p]$
where $i$ and $p$ are unique identifiers of the argument itself and its parent, respectively.
For convenience, we define the set containing the identifiers of all children and siblings of a node $\Node[i][p]$ by $\Children[i]$ and $\Siblings[i]\equiv\Children[p]$

%Depending on if one argument can point to one or multiple other nodes,
%this results in a tree graph or a directed acyclic graph.
%\todo{Jede verlinkung/edge ist ein eigener Rating market}

@@

%or links to a curated knowledge graph (see the underlay \cite{UNDERLAY}).

%\subsection{Establishing a Link to the Knowledge Graph}
%\cite{Hogan2020}
%Rational decision-making:
%establish a link between the decision and knowledge by a directed argument graph.
%
%-> this derives important features
%The longer the argument chain, the less influence has the knowledge
%
%%OR - curation of arguments

@@

%\begin{figure*}
%	Stakeholders
%	\caption{Text}
%	\label{fig:Tree}
%\end{figure*}

\section{Phases, Stakeholders, and Stakes of the Debate}\label{sec:DebatingProcess}

% Motivate formalization before?

The decision-making process in ArborVote consists of three phases:
\begin{enumerate}[noitemsep]
	\item editing (with an grace period for each author subtree)
	\item rating
	\item tallying
\end{enumerate}
in which participants can occupy one or multiple of the roles listed below
\begin{itemize}[noitemsep]
	\item debaters
	\item curators
	\item jurors
	\item voters
\end{itemize}
In the following, these roles are briefly presented.
Debaters author arguments or fact nodes and add them to the debate tree.
Curators can flag and propose edits to the content that authors can accept or reject.
In the latter case, a dispute is raised that is resolved by jurors in a digital court.
Lastly, voters can invest \debateTokens{} to rate the impact of nodes in the debate tree.
To maintain neutrality, jurors are excluded from the other roles.

% Debate Tokens
\todo{Move elsewhere}
In this system, 
each participant has a predefined amount of \debateTokens{} $\T$ that can only be spend within the debate.
These are either distributed equally among the participants or based on the reputation in the \ac{DAO}.
%
Participants can spend the \debateTokens{} 
to create, curate, and rate arguments.
%
The system rewards participants behaving deliberate- and constructively in the debate
, which is described in\replaced{the following}{ \cref{sec:Incentives}}.

@@

Within a predefined grace-period, an argument owner can edit the argument or post sub-nodes, 
whereas other participants cannot.
However, other participants can suggest edits, moving, or removal of the argument in which case they are called curators.

@@

\subsubsection*{Ownership, Curation, and Dispute Resolution}
%Despite suggesting edits or removal of arguments,
Disputes about argument ownership might arise, 
if duplicates or very similar statements are present in different parts of the tree.
%
Curators can flag nodes that contain
\begin{itemize}[noitemsep]
\item plagiarism, 
\item spam, or 
\item offensive content such as hate-speech or sexism.
\end{itemize}

These participants are called curators and have to lock up a deposit, 
i.e, tokens that have monetary value and are not \debateTokens{}, 
in order to raise a dispute. 
If the argument author agrees with the accusation, he/she can remove the argument \replaced{and pac only a small}{without any} penalty \added{to the curator}.
If not, the author has to match the deposit and the dispute is escalated to a digital court such as \href{https://kleros.io/}{Kleros Court}\cite{Lesaege2019,Lesaege2021} or \href{https://anj.aragon.org/}{Aragon Court}\cite{Cuende2019}.

@@

\subsection{Rating Phase}\label{sec:RatingPhase} % Voting Phase

After the editing phase ended and the argument tree is completely finalized,
the debate enters the rating phase---the actual voting process.

% challenge
% Design rationale
\highlight{The key game-theoretical challenge} here is to incentivize the participants to 
rate the impact $\imp$ of an argument or fact node
and to decouple it from the individual outcome preference or in simple terms: to eliminate tactical voting.
Voting solely with the goal to influence the decision should be a unprofitable long-term strategy.

\todo{How is the design rational achieved?}
% Rating markets
This design rationale can be achieved by employing a market mechanism---we call this a \ac{RM}.
%This impact is determined separately for each argument via a market mechanism that we call \ac{RM}.
A \ac{RM} is a slightly modified \ac{PM} such as the \href{https://omen.eth.link/}{Omen \ac{PM}}\cite{Omen2020} and also uses an \ac{AMM}\cite{Zhang2018} for liquidity provision.

Participants can spend their \debateTokens{} to invest in approval or disapproval shares $\Y$ and $\T$
\deleted{being minted at the current market ratio}.
These participants are called voters.

@@

% PM contrast
In contrast to a conventional \ac{PM} where all shares except that of the correctly predicted outcome (determined by an oracle) are invalidated after the market close,
all shares maintain their last value and are redeemed for \debateTokens. 
\todo{How to prevent unwanted dynamics shortly before the market close?}
% Arbitrage
%\replaced{
%	In said system, voters can spend their \debateTokens{} $\T$
%	and swap them for approval ($\Y$) or disapproval ($\N$) shares on the argument market.
%	Depending on if the \ac{RM} has moved in the opposite direction at the point if its close, 
%	participants gain or lose tokens.
%		This is can be a profitable or unprofitable trade.
%}{
	Accordingly, voters who buy approval or disapproval shares of under- or overrated arguments that turn out to be rated higher or lower at the market close, respectively, make a profit in \debateTokens.
%}

% Liquidity provision by the author
The liquidity of the \ac{AMM} is provided by the author of the argument who has to deposit \debateTokens{} at the point of the creation of the argument.
Moreover, the author determines the initial amount of the approval and disapproval shares $r^\Y$ and $r^\N$ minted from the \debateTokens{} at the market start
and therefore the initial impact $\imp$.
If the argument creator does not specify a ratio, 
the amount of approval and disapproval tokens is set with $r^\Y=r^\N=\nicefrac{1}{2}\,r^\T$. 
% Fees and Permanant Loss
As in every \ac{AMM}, liquidity providers (here the author \todo{and editors of the argument})
earn fees of traders (here voters)
and 
take the risk of suffering permanent loss, if the market diverges from the initial value.
This incentivizes authors to evaluated their own arguments impact critically 
\deleted[comment={Should the final earning/loss be related to $a$ or $a'$}]{and to take also related child arguments into account}
to minimize permanent loss. 
% Initial impact
To disincentivizes debaters to create bad arguments and earn on the fees,
the initial ratio is limited to $[\nicefrac{1}{2},1)$ (or even a more conservative lower limit $>\nicefrac{1}{2}$).
The value $\imp=1$ is excluded because otherwise, the constant product $\Y\times \N = 0$.
% RM details
The details of the rating market mechanics are discussed in detail in \cref{sec:RatingMarkets}

@@

\subsection{Tallying Phase}\label{sec:TallyingPhase}
In the tallying phase, the impact of the different nodes is accumulated and weighted.
We define the weight of a node $\Node[i]$ by
\begin{equation}
	%\wgt[i] = \frac{\liq[i]}{\liq[i][\sib]}
	\wgt[i][\Siblings] = \frac{\liq[i]}{\sum_{j\in \Siblings[i]}\liq[j]}
\end{equation}
as the 
amount of \debateTokens{} spent on node $\Node[i]$, $\liq[i]$,
in relation to all its siblings $\Siblings[i]$.

to the total number of deposited \debateTokens{} of its siblings.
This allows for expressing the impact of a node $\Node[i]$ 
\begin{equation}\label{eq:Impact}
	\imp[i] = 
	\max
	\left[\vphantom{\sum}\right.
	0
	\,,\,
	\underbrace{(1-\mixing[i])\cdot\impOwn[i]}_{\text{own}} 
	+
	\underbrace{\mixing[i]\cdot\imp[i][\Children]}_{\text{children}}
	\left.\vphantom{\sum}\right],
\end{equation}
as two terms scaled with a mixing parameter $\gamma$.
The $\max$ operator ensures, that the impact value cannot become negative.

The first term $\impOwn[i]$ is the nodes own impact determined directly from the associated \ac{RM}.
The other term contains the impact influence exerted by the children nodes
\begin{equation}
	\imp[i][\Children] = \sum_{j\in \Children[i]} \supportive[j][i] \imp[j]\,\wgt[j][\Siblings],
\end{equation}
being weight-averaged by the sibling-weight impact of all children nodes
\deleted{which recurses from the root to the leaf level of the argument tree,}.
and a prefactor
\begin{equation}
	\supportive[j][i]=
	\begin{cases}
		+1 & \text{if node $j$ supports node $i$}\\
		-1 & \text{if node $j$ \,opposes\, node $i$}\\
	\end{cases},
\end{equation}
leading to the subtraction of impact, if the node is opposing.
% Mixing
Both terms are scaled with the mixing parameter $\gamma$.
The higher the value of $\gamma$, the more influence the children nodes have on $\imp[i]$

Special cases arise for the different node types in the tree:
\begin{equation}
	\mixing[i] =
	\begin{cases}
		1 & \text{if $\Node[i]$ is root ($i=0$)}\\
		0 & \text{if $\Node[i]$ is leaf}\\
		k \in[\nicefrac{1}{2},1) & \text{else}
	\end{cases}
\end{equation}
% root
For the root node, the impact is solely determined from the children's approval  ($\mixing=1$).
% leaf
For a leaf node, the impact is determined solely from its own rating market ($\mixing=0$).
% all others
For all other nodes,
the ratio between the two is defined by to a constant $k\in[\nicefrac{1}{2},1)$.

\todo{Add example.\\ 
For example with $k=\nicefrac{3}{4}$...}

\todo{
\section{Incentive Structures}\label{sec:Incentives}
% Creation

\subsection{Rewards}
- debate summoner has to offer rewards (either reputation or money)

- rewards are split between participants that performed above average
}

@@

\subsection{Spamming Attacks}
The number of nodes that can be created is limited by the number of \debateTokens{} and
curators can remove the spam nodes.

@@

\subsection{Sybil-Attacks}
Ensure that users are real humans by employing curated registries such as \href{https://proofofhumanity.id/}{Proof of Humanity}.

\subsection{Collusion}
Todo
\todo{
	What types of collusion are possible and
	can they be prevented by utilizing \ac{MACI}?
}

@@

\subsection*{Rating Markets}\label{sec:RatingMarkets}

An \ac{AMM} is used to provide liquidity for the rating markets.

\todo{
	Contrast to \ac{PM}:
	half as many shares are minted so that one share is allocated for each \highlight{collateralized} \debateTokens
	instead of two.
}

\todo{
	This impact of each node is influenced by two quantities:
	the approval $\imp$ and \highlight{weight} $\wgt$.
}

The argument creator uses $r^\T$ \debateTokens{} 
to mint 
$r^\Y$ approval ($\Y$) and 
$r^\N$ disapproval ($\N$) shares
%at a price ratio
%\begin{equation}
%	\label{eq:PriceRatio}
%	p = \frac{r^\Y}{r^\N}
%\end{equation}
so that
\begin{equation}
	r^\Y+r^\N = \liq.
\end{equation}
The $Y$ and $N$ tokens form a trading pair
that has to maintain a constant value
\begin{equation}
	k = r^\Y\cdot r^\N
\end{equation}

If a voter invests \debateTokens{} to buy, e.g., approval shares,
both share types are minted at the \highlight{current} \ac{AMM} ratio of $r^\Y: r^\N$.
Then, the unwanted shares are sold at the \ac{AMM} for the wanted share type, 
which is the same implementation as in 
\href{https://omen.eth.link/}{Omen \acp{PM}}\cite{Omen2020}.
\todo{
	%Use this for curators that suggest edits?
	The value k can change if more LPs join
	\begin{equation}
		\sum_i w_i \, p_i = k
	\end{equation}
}
An example is depicted in \cref{fig:RatingMarket}.
\begin{figure*}
	\includegraphics[width=0.75\textwidth]{Graphics/RatingMarket.pdf}
	\caption{Process flow diagram in a rating market showing
	(1) liquidity provision by the argument creator Carl with a ratio of $r^\Y:r^\N=1$
	and 
	(2,3) two consecutive market trades by Alice and Bob where each of them buys approval shares for an equivalent of 2\,\T{} on the underlying \ac{AMM}.
	After the market close, 
	Alice and Bob redeem their approval shares \Y{} for \num[round-mode=places,round-precision=1]{2.534597515403166}
	and
	\num[round-mode=places,round-precision=1]{2.0801261686545804}
	\debateTokens{} \T{}, thus generating profit.
	Carl redeems his \Y{} and \N{} shares for
	$\num[round-mode=places,round-precision=1]{4.813525792017222}\,\T
	+\num[round-mode=places,round-precision=1]{4.571750523925031}\,\T
	=\num[round-mode=places,round-precision=1]{9.3852763159}\,\T$, thus suffering a loss.
}
	\label{fig:RatingMarket}
\end{figure*}

>>>>

\newcommand{\T}{\text{T}}
\newcommand{\Y}{\text{Y}}
\newcommand{\N}{\text{N}}

@@

\begin{acronym}
	\acro{AMM}{automated market maker}
	\acro{CPMM}{constant product market maker}
	\acro{PM}{prediction market}
	\acro{RM}{rating market}
	\acro{DAPP}{decentralized application}
	\acro{DAO}{decentralized autonomous organization}
	\acro{DLT}{distributed ledger technology}
	\acroplural{DLT}[DLTs]{distributed ledger technologies}
	\acro{DAG}{directed acyclic graph}
	\acro{MACI}{minimal anti-collusion infrastructure}
	\acro{L2}{layer 2}
\end{acronym}

@@

% Why Blockchain
Since digital debating platforms (such as \href{https://www.kialo.com/}{kialo} do exist online,
the question might arise why \acp{DLT} are needed to construct and execute a decision from a debate.
%
Three requirements favor the usage of \acp{DLT}.
% Tamper-Proof Infrastructure
First and foremost, voting processes require a tamper-proof and permissionless infrastructure that cannot be guaranteed with centralized technologies.
% Sybil protection
A second requirement is Sybil protection. 
Curated registries of unique digital identities are already available on several blockchains. 
% Incentivization
A last and optional requirement is the ability to incentivize participation.
Because the time and collective attention of the people are scarce resources,
the ability to allocate reputational or monetary rewards is useful
and especially easy to realize in the form of blockchain tokens.
To put this rather economic view in perspective:
One might see this deliberative decision-making as the decentralization of the job of politicians and consultants that are also getting paid.

@@

\section{Structuring Debates in Argument Graphs}\label{sec:Structure}
The reasoning behind making a decision is rarely linear. 
Most of the time debates consist of numerous, interdependent arguments 
originating from the root node and  branching off multiple times. 
This results in a tree structure as depicted in \cref{fig:Tree},
where arguments \highlight{(or facts)} constitute the nodes in the tree.
Three node types exist in this tree graph: 
root, argument, and fact nodes. 
Nodes without child nodes below them are called leaves.

\begin{figure}
	\resizebox{0.95\linewidth}{!}{
		\includegraphics{Graphics/Tree.tikz}
	}
	\caption{
		Visualization of a debate as an argument tree with 
		the root node $\Root$ (dotted), 
		argument nodes $\Arg$ (solid), and 
		fact nodes $\Fact$ (dashed) 
		numbered by their order of creation.
		Nodes have an impact $\imp$ and a weight $\wgt$ relative to their siblings 
		and can support or oppose their associated parent as indicated by green and red links, respectively.
	}
	\label{fig:Tree}
\end{figure}

\subsection{Root Nodes}
The decision option forms the root $\Root$ of the tree and is expressed as a statement, 
e.g., 'We should execute process A.', 
that can be \replaced{approved}{supported} or \replaced{disapproved}{opposed} by the participants of the debate in the voting process.
%
To facilitate multiple decision options, 
multiple trees can be constructed---all of them having their own root statement, 
e.g., 'We should execute process B.'.

\subsection{Argument Nodes}
Participants of the debate can create arguments $\Arg$ below the root
or other arguments. 
%
Within a debate, each argument points to one parent node (either the root or another argument) it is referring to.

To identify each node $\Node$ in the tree, the notation $\Node[i][p]$ is used, 
where $i$ and $p$ are unique identifiers of the argument itself and its parent, respectively.
For convenience, we define the set containing the identifiers of all children and siblings of a node $\Node[i][p]$ by $\Children[i]$ and $\Siblings[i]\equiv\Children[p]$

@@

@@

\section{Phases, Stakeholders, and Stakes of the Debate}\label{sec:DebatingProcess}
\todo{Motivate formalization before?}

The decision-making process in ArborVote consists of three phases:
\begin{enumerate}[noitemsep]
	\item editing
	\item rating
	\item tallying
\end{enumerate}
in which participants can occupy one or multiple of the roles listed below
\begin{itemize}[noitemsep]
	\item debaters
	\item curators
	\item jurors
	\item voters
\end{itemize}
In the following, these roles are briefly presented.
Debaters author arguments or fact nodes and add them to the debate tree.
Curators can flag and propose edits to the content that authors can accept or reject.
In the latter case, a dispute is raised that is resolved by jurors in a digital court.
Lastly, voters can invest debate tokens to rate the impact of nodes in the debate tree.
To maintain neutrality, jurors are excluded from the other roles.

% Debate Tokens
\todo{Move elsewhere}
In this system, 
each participant has a predefined amount of debate tokens $\T$ that can only be spend within the debate.
These are either distributed equally among the participants or based on the reputation in the \ac{DAO}.
%
Participants can spend the debate tokens 
to create, curate, and rate arguments.
%
The system rewards participants behaving deliberate- and constructively in the debate
, which is described in\replaced{the following}{ \cref{sec:Incentives}}.

@@

Within a predefined grace-period, an argument owner can edit the argument or post sub-nodes, 
whereas other participants cannot.
However, other participants can suggest edits, moving, or removal of the arguments and are thus called curators.

@@

\subsubsection*{Ownership, Curation, and Dispute Resolution}
%Despite suggesting edits or removal of arguments,
Disputes about argument ownership might arise, 
if duplicates or very similar statements are present in different parts of the tree.
Curators can flag nodes containing 
plagiarism, 
spam, or 
offensive content such as hate-speech or sexism. 
In order to raise a dispute, 
curators have to lock up a deposit, 
i.e, tokens that have monetary value and are not debate tokens. 
If the argument author agrees with the accusation, he/she can remove the argument \replaced{and pay only a small}{without any} penalty of the deposited debate tokens \added{to the curator}. 
If not, the author has to match the deposit and the dispute is escalated to a digital court such as \href{https://kleros.io/}{Kleros Court}\cite{Lesaege2019,Lesaege2021} or \href{https://anj.aragon.org/}{Aragon Court}\cite{Cuende2019}.

@@

\subsection{Rating Phase}\label{sec:RatingPhase} % Voting Phase
After the editing phase ended and the argument tree is completely finalized,
the debate enters the rating phase---the actual voting process.

% challenge
% Design rationale
\highlight{The key challenge} here is to incentivize the participants to 
rate the impact $\imp$ of an argument or fact node
and to decouple it from the individual outcome preference. 
In simple terms: to eliminate tactical voting.
Voting solely with the goal to influence the decision should be a unprofitable long-term strategy.

% Rating markets
This design rationale can be achieved by employing a market mechanism---we call this a \ac{RM}.
%This impact is determined separately for each argument via a market mechanism that we call \ac{RM}.
A \ac{RM} is a slightly modified \ac{PM} such as the \href{https://omen.eth.link/}{Omen \ac{PM}}\cite{Omen2020} and also uses an \ac{AMM}\cite{Zhang2018} for liquidity provision.
Participants can spend their debate tokens to invest in approval or disapproval shares $\Y$ and $\N$
\deleted{being minted at the current market ratio}.
These participants are called voters.

@@

% PM contrast
In contrast to a conventional \ac{PM} where all shares except that of the correctly predicted outcome (determined by an oracle) are invalidated after the market close,
all shares maintain their last value and are redeemed for debate tokens. 
\todo{How to prevent unwanted dynamics shortly before the market close?}
% Arbitrage
Accordingly, voters who buy approval or disapproval shares of under- or overrated arguments that turn out to be rated higher or lower at the market close, respectively, make a profit in debate tokens.

% Liquidity provision by the author
The liquidity of the \ac{AMM} is provided by the author of the argument who has to deposit debate tokens at the point of the creation of the argument.
Moreover, the author determines the initial amount of the approval and disapproval shares $r^\Y$ and $r^\N$ minted from the debate tokens at the market start
and therefore the initial impact $\imp$.
If the argument creator does not specify a ratio, 
the amount of approval and disapproval tokens is set with $r^\Y=r^\N=\nicefrac{1}{2}\,r^\T$. 
% Fees and Permanant Loss
As in every \ac{AMM}, liquidity providers (here the author \todo{and editors of the argument})
earn fees of traders (here voters)
and 
take the risk of suffering permanent loss, if the market diverges from the initial value.
This incentivizes authors to evaluated their own arguments impact critically 
\deleted[comment={Should the final earning/loss be related to $a$ or $a'$}]{and to take also related child arguments into account}
to minimize permanent loss. 
% Initial impact
To disincentivizes debaters to create bad arguments and earn on the fees,
the initial ratio is limited to $[\nicefrac{1}{2},1)$ (or even a more conservative lower limit $>\nicefrac{1}{2}$).
The value $\imp=1$ is excluded because otherwise, the constant product $\Y\times \N = 0$.
% RM details
The details of the rating market mechanics are discussed in detail in \cref{sec:RatingMarkets}

@@

\subsection{Tallying Phase}\label{sec:TallyingPhase}
In the tallying phase, the impact of the different nodes is accumulated and weighted.
We define the weight of a node $\Node[i]$ by
\begin{equation}
	%\wgt[i] = \frac{\liq[i]}{\liq[i][\sib]}
	\wgt[i][\Siblings] = \frac{\liq[i]}{\sum_{j\in \Siblings[i]}\liq[j]}
\end{equation}
as the 
amount of debate tokens spent on node $\Node[i]$, $\liq[i]$,
in relation to all its siblings $\Siblings[i]$.

to the total number of deposited debate tokens of its siblings.
This allows for expressing the impact of a node $\Node[i]$ 
\begin{equation}\label{eq:Impact}
	\imp[i] = 
	\max
	\left[\vphantom{\sum}\right.
	0
	\,,\,
	\underbrace{(1-\mixing[i])\cdot\impOwn[i]}_{\text{own}} 
	+
	\underbrace{\mixing[i]\cdot\imp[i][\Children]}_{\text{children}}
	\left.\vphantom{\sum}\right],
\end{equation}
as two terms scaled with a mixing parameter $\gamma$.
The $\max$ operator ensures, that the impact value cannot become negative.

The first term $\impOwn[i]$ is the nodes own impact determined directly from the associated \ac{RM}.
The other term contains the weight-averaged impact of all children nodes 
\begin{equation}
	\imp[i][\Children] = \sum_{j\in \Children[i]} \supportive[j]%[i] 
	\imp[j]\,\wgt[j][\Siblings].
\end{equation}
with the prefactor
\begin{equation}
	\supportive[j]%[i]
	=
	\begin{cases}
		+1 & \text{if node $j$ is supporting}\\ %node $i$}\\
		-1 & \text{if node $j$ is opposing} %\, node $i$}\\
	\end{cases},
\end{equation}
resulting in the subtraction of impact, if the associated node is opposing.
% Mixing
Both terms are scaled with the mixing parameter $\mixing$.
The higher the value of $\mixing$, the more influence the children nodes have on $\imp[i]$.
Because the influence of a single node on the decision outcome decreases with increasing distance from the tree root, 
it becomes less attractive to add too many layers to the tree, which incentivizes keeping debates short.

Special cases arise for the different node types in the tree:
\begin{equation}
	\mixing[i] =
	\begin{cases}
		1 & \text{if $\Node[i]$ is root ($i=0$)}\\
		0 & \text{if $\Node[i]$ is leaf}\\
		k \in[\nicefrac{1}{2},1) & \text{else}
	\end{cases}
\end{equation}
% root
For the root node, the impact is solely determined from the child impacts  ($\mixing=1$).
% leaf
For a leaf node, the impact is determined solely from its own rating market ($\mixing=0$).
% all others
For all other nodes,
the ratio between the two is defined by constant $k\in[\nicefrac{1}{2},1)$ specified by the debate creator.

\todo{Add example.\\ 
For example with $k=\nicefrac{3}{4}$...
}

\todo{
\section{Incentive Structures}\label{sec:Incentives}
% Creation
\subsection{Rewards}
- debate summoner has to offer rewards (either reputation or money)
- rewards are split between participants that performed above average
}

@@

\subsection{Spamming Attacks}
The number of nodes that can be created is limited by the number of debate tokens and
curators can remove the spam nodes.

@@

\subsection{Sybil-Attacks}
Curated registries such as \href{https://proofofhumanity.id/}{Proof of Humanity}
ensure that only real humans participate.

\subsection{Collusion}
Collusion (such as bribery or blackmailing) is still an open problem in decentralized governance.
However, it can be solved in the future if \ac{MACI}\cite{Buterin2021} becomes available.
In the context of ArborVote this means that the debate participants remain secret and cannot proof to each other that they have created or voted for a certain tree node.

@@

\subsection*{Rating Markets}\label{sec:RatingMarkets}
An \ac{AMM}, more specifically a \ac{CPMM}, is used to provide liquidity for the rating markets.
The argument creator deposits $r^\T$ debate tokens 
to mint 
$r^\Y$ approval ($\Y$) and 
$r^\N$ disapproval ($\N$) shares
%at a price ratio
%\begin{equation}
%	\label{eq:PriceRatio}
%	p = \frac{r^\Y}{r^\N}
%\end{equation}
so that
\begin{equation}
	r^\Y+r^\N = \liq.
\end{equation}
The $\Y$ and $\N$ tokens form a trading pair
whose product has to remain constant
\begin{equation}
	k = r^\Y\cdot r^\N.
\end{equation}

If a voter invests debate tokens to buy, e.g., approval shares,
both share types are minted at the \highlight{current} \ac{AMM} ratio of $r^\Y: r^\N$.
Then, the unwanted shares are sold at the \ac{AMM} for the wanted share type, 
which is the same implementation as in 
\href{https://omen.eth.link/}{Omen \acp{PM}}\cite{Omen2020}.
An example is depicted in \cref{fig:RatingMarket}.
\begin{figure*}
	\includegraphics[width=0.75\textwidth]{Graphics/RatingMarket.pdf}
	\caption{Process flow diagram in a rating market showing
	1.) liquidity provision by the argument creator Carl with a ratio of $r^\Y:r^\N=1$
	and 
	two consecutive market trades by 
	2.) Alice and 
	3.) Bob where each of them buys approval shares for an equivalent of 2\,\T{} on the underlying \ac{CPMM}.
	After the market close, 
	Alice and Bob redeem their approval shares \Y{} for \num[round-mode=places,round-precision=1]{2.534597515403166}
	and
	\num[round-mode=places,round-precision=1]{2.0801261686545804}
	debate tokens \T{}, thus generating profit.
	Carl redeems his \Y{} and \N{} shares for
	$\num[round-mode=places,round-precision=1]{4.813525792017222}\,\T
	+\num[round-mode=places,round-precision=1]{4.571750523925031}\,\T
	=\num[round-mode=places,round-precision=1]{9.3852763159}\,\T$, thus suffering a loss.
}
	\label{fig:RatingMarket}
\end{figure*}
